A Search for Supernova Remnants in NGC\,6946

### 2018-11-04 ms.tex
Updates to get all of the lines in the tables to appear

The SNR candidates are listed in Table \ref{table_candidates}.

@@

@@

%% To help institutions obtain information on the effectiveness of their 
%% telescopes the AAS Journals has created a group of keywords for telescope 
%% facilities.
%
%% Following the acknowledgments section, use the following syntax and the
%% \facility{} or \facilities{} macros to list the keywords of facilities used 
%% in the research for the paper.  Each keyword is check against the master 
%% list during copy editing.  Individual instruments can be provided in 
%% parentheses, after the keyword, but they are not verified.

>>>>

The SNR candidates are listed in right ascension order in Table \ref{table_candidates}.  For each candidate, we provide (1) a source name, (2) the name of the source in MF97 if any,  (3,4) the position  (J2000), (5) the galactocentric radios, (6) the \ha flux as derived from the emission line images, (7) the [SII]:\ha\ ratio measured from the images, (8) the spectrum we used to confirm the imaging ratios (see below) , and (9) whether or not the object had a spectroscopic [SII]:\ha\ ratio greater than 0.4.

@@

\startlongtable

@@

\pagebreak
%% To help institutions obtain information on the effectiveness of their 
%% telescopes the AAS Journals has created a group of keywords for telescope 
%% facilities.
%
%% Following the acknowledgments section, use the following syntax and the
%% \facility{} or \facilities{} macros to list the keywords of facilities used 
%% in the research for the paper.  Each keyword is check against the master 
%% list during copy editing.  Individual instruments can be provided in 
%% parentheses, after the keyword, but they are not verified.
